Opt-K

### 2013-03-13 paper/paper.tex
updated paper

\usepackage{amsmath}    % need for subequations
\usepackage{amssymb}    % for symbols
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs

@@

To compute the fractional volumes of the Voronoi cells, we use the following randomized algorithm. First, we generate points inside of the bounding region using the lazy walker markov chain monte carlo algorithm.

% Computing both N-dimensional Voronoi volumes and convex hulls is
% difficult too. We adopt the following approximate algorithm. First, we
% compute the axis-aligned bounding box of all of the conformations. Next,
% we fit a multi-dimensional gaussian to the coordinates of each state.
% (We should probably use a diagonal covariance matrix, or even a
% spherical gaussian?).

Now, we sample random points from the uniform distribution over the
bounding box. We check these points against all of the gaussian PDFs. If
the point is farther than $3\sigma$ away from every cluster
center, we reject it, reasoning that it is probably outside the convex
hull. The remaining points are now a representation of the uniform
distribution over the convex hull of phase space. For each point, we
compute its distance to each of the cluster centers, ``assigning'' it to
the center it is closest to. As the number of randomly sampled points
goes to infinity, the fraction of the points assigned to each state
converges to being proportional to the state's volume.

This algorithm is highly amenable to parallel computation. For a euclidean
distance metric, the assignment can be sped up by using a BallTree data
structure for fast neighbor search. (We can probably actually use this
data structure within msmbuilder's assign step...)

The documentation for the sklearn cython BallTree is given here \url{http://scikit-learn.org/dev/modules/generated/sklearn.neighbors.BallTree.html#sklearn.neighbors.BallTree}

@@

Choose both the clustering algorithm (k-centers, k-means, etc) and the
number of states by maximizing the BIC score of the model, using this
likelihood.

Unfortunately, this doesn't really help with picking the projection operator
to vectorize the conformations (e.g. dihedrals, contact maps, etc). Also,
it's not going to work with RMSD.

>>>>

\usepackage{amsmath}    % need for subequations
\usepackage{amssymb}    % for symbols
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
%\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs

@@

To compute the fractional volumes of the Voronoi cells, we use the following randomized algorithm. First, we generate points inside of the bounding region using the lazy random walk Markov chain Monte Carlo algorithm.\cite{Kannan97} This random walk converges to sampling from the uniform distribution over the interior. After a sufficient burn in period, for each sampled point we compute its nearest MSM state center, assigning it to that state. As the number of randomly sampled points goes to infinity, the fraction of the points assigned to each state converges to being proportional to the state's volume.

This algorithm is highly amenable to parallel computation. For a euclidean
distance metric, the assignment can be performed efficiently by using a BallTree 
data structure for fast neighbor search.

@@

We choose both the clustering algorithm (k-centers, k-means, etc) and the
number of states by maximizing the BIC/AIC scores of the model, using this
likelihood.

Unfortunately, this doesn't really help with picking the projection operator
to vectorize the conformations (e.g. dihedrals, contact maps, etc). Also,
it's not going to work rigorously with RMSD.

\section{Validation}
We being by using the procedure described above on the M\"{u}ller potential.
